Clause size reduction with all-UIP Learning

### 2020-02-27 paper.tex
update optimized proof checking size counting only mutally solved instances

\subsubsection{Clause Reduction with $\allUip$.}
To precisely measure $\allUip$'s clause reduction power, we compare
each instance's learnt clause size from $\allUipMin$ and $\allUipPure$
against 1-UIP. Fig.~\ref{fig:len_pdf} shows the probability density
distribution (PDF) of the relative clause size of the $\allUip$
learning schemes ($\allUipMin$ in green and $\allUipPure$ in red) for
each instance. $\allUipMin$ ($\allUipPure$ resp.) produces shorter
clauses for 88.5\% (77.7\%) of instances, and the average relative
reduction ratio over 1-UIP is 18.6\%
(16.7\%). Fig.~\ref{fig:len_compare} compares the average learnt
clause size of $\allUipMin$, $\allUipPure$ and 1-UIP per instance.
Both $\allUip$ schemes generally yield smaller clauses, and the size
reduction is more significant for instances with larger 1-UIP clauses.

@@

The average optimized DRAT proof from $\allUipMin$ and $\allUipPure$
are 556.6MB and 654.4MB, respectively. Both sizes are significantly
smaller than the average optimized proof size from 1-UIP, 824.9MB.
The average proof size reduction per instance for $\allUipMin$ and
$\allUipPure$ was 16.5\% and 4.6\% compared with 1-UIP, which roughly
correlate with our observed clause size observation in
Fig~\ref{fig:len_pdf}.

>>>>

\subsubsection{Clause Reduction with $\allUip$.}
To precisely measure $\allUip$'s clause reduction power, we compare
each instance's learnt clause size from $\allUipMin$ and $\allUipPure$
against 1-UIP. Fig.~\ref{fig:len_pdf} shows the probability density
distribution (PDF) of the relative clause size of the $\allUip$
learning schemes ($\allUipMin$ in green and $\allUipPure$ in red) for
each instance. $\allUipMin$ ($\allUipPure$ resp.) produces shorter
clauses for 88.5\% (77.7\%) of instances, and the average relative
reduction ratio over 1-UIP is 18.5\%
(9.6\%). Fig.~\ref{fig:len_compare} compares the average learnt
clause size of $\allUipMin$, $\allUipPure$ and 1-UIP per instance.
Both $\allUip$ schemes generally yield smaller clauses, and the size
reduction is more significant for instances with larger 1-UIP clauses.

@@

The average optimized DRAT proof from $\allUipMin$ and $\allUipPure$
are 556.6MB and 698.5MB, respectively. Both sizes are significantly
smaller than the average optimized proof size from 1-UIP, 824.9MB.
The average proof size reduction per instance for $\allUipMin$ and
$\allUipPure$ was 16.5\% and 3.6\% compared with 1-UIP, which roughly
correlate with our observed clause size observation in
Fig~\ref{fig:len_pdf}.
